\documentclass[8pt]{extarticle}

\usepackage[top=.5in,
            bottom=.5in,
            left=.5in,
            right=.5in]{geometry}

\usepackage{microtype}

\usepackage[T1]{fontenc}
\usepackage[ascii]{inputenc}

\usepackage{amsmath, amssymb}
\usepackage{mathtools}

\usepackage{tikz}

\usepackage{fancyhdr}

%\usepackage{showframe}

\setlength{\headheight}{.75in}

\fancypagestyle{resume}{
    \fancyhf{}
    \chead{\textbf{Kye W. Shi} \\ \small 340 E Foothill Blvd, Box 705 \\ Claremont, CA 91711}
    \lhead{\small \texttt{kwshi@hmc.edu} \\ \texttt{github.com/kwshi}}
    \rhead{\small (630) 824-7713}
}

\pagestyle{resume}

\usepackage{titlesec}

\usepackage{enumitem}

\usepackage{tabularx}

\usepackage{array}

\usepackage{multicol}

\makeatletter
\newcommand{\compress}{\@minipagetrue}
\makeatother

\usepackage{parskip}

\newcommand{\location}[1]{(#1)}
\newcommand{\name}[1]{\textbf{#1}\hspace{1em}}
\newcommand{\cat}[1]{#1:}


\renewcommand{\arraystretch}{.25}

\begin{document}



\begin{center}
\begin{tabularx}{\textwidth}{>{\scshape}r >{\compress}X | >{\footnotesize\scshape}l}

Education 

&

\name{Harvey Mudd College} \location{Claremont, CA}

B.S. in Mathematics \& Computer Science

\cat{Relevant coursework} 
\begin{itemize}
\item Principles \& Practice of Computer Science 
\item Multivariable Calculus
\item Computability \& Logic
\end{itemize}

&

Aug. 2017--(May 2021)

\\

&

\name{Monte Vista Christian School} \location{Watsonville, CA}

Salutatorian, GPA 4.5 (unweighted 4.0)

\cat{Relevant coursework}
\begin{multicols}{2}
\begin{itemize}
\item Digital Electronics
\end{itemize}
\end{multicols}

&

Aug. 2013--May 2017

\\

Skills

&

\cat{Languages}

Fluent: Python, \LaTeX
Familiar: Go, Bash, HTML/CSS
Basic: Java, Javascript, Rust, C/C++

\cat{Software} \compress
\begin{multicols}{2}
\begin{itemize}
\item Arch Linux (home, servers)
\item OpenSCAD (personal projects)
\item Arduino (personal projects)
\item Raspberry Pi (mini servers)
\end{itemize}
\end{multicols}

\\

Experience

&

\name{Tutoring}

Unpaid tutoring for high school peers in physics, economics, and mathematics

Paid tutoring over Skype for high school students in olympiad-level physics

&

2015--Present

\\

&

\name{iOS Development}

Development of ``Totem'' app, comprehensive chemical elements database

&

Sep.--Nov. 2014

\\

Activities

&

\name{Yale Summer Program in Astrophysics} \location{New Haven, CA}

4-week research project in near-earth asteroid trajectory/collision prediction

\cat{Relevant skills}
\begin{multicols}{2}
\begin{itemize}
\item Asteroid observation 
\item Asteroid trajectory regression
\item Python (NumPy, SciPy)
\item Statistical data analysis 
\item Basic genetic algorithms
\end{itemize}
\end{multicols}

&

Jul.--Aug. 2016

\\

&

\name{MathILy} \location{Bryn Mawr, PA}

5-week inquiry-based mathematics exploration summer program

\cat{Relevant topics}
\begin{multicols}{2}
\begin{itemize}
\item Linear algebra
\item Abstract algebra
\item Graph theory
\item Complex analysis
\item Knot theory
\item Projective geometry
\item Number theory
\item Applications in origami
\end{itemize}
\end{multicols}

&

Jul.--Aug. 2015, Jul. 2016

\\

&

\name{U.S. Physics Traveling Team} \location{Baltimore, MD / Indonesia}

10-day training camp in introductory modern physics, theory and experiment

Participation in 2017 International Physics Olympiad representing the U.S.

&

Jun. 2017



\\

Leadership

&

\name{VEX Robotics} \location{High school}

Lead programmer, programming mentor for teammates

&

Sep. 2016--Feb. 2017

\\

&

\name{3D Printing Consultant} \location{High school}

Installation and maintenance of 3d printer for engineering design class

&

2015--2017

\\

Achievements

&

\name{U.S. National Physics Olympiad}  Gold medal

&

Apr. 2016, 2017

\\

&

\name{ACM Intercollegiate Programming Competition (ICPC)} Southern California regional qualifier

&

Nov. 2017

\\

&

\name{International Physics Olympiad} Gold medal

&

Jul. 2017

\\

&

\name{American Mathematics Competition} AIME qualifier

&

Mar. 2016, 2017






\end{tabularx}
\end{center}







\end{document}
